Idea Development

### 2024-11-10 posts/Abortion/abortion.qmd
abortion
remove wecount link

-   “All telehealth abortions are counted according to **the state the medications are mailed to**.” This approach of defining and counting telehealth aborting is used by [WeCount](https://societyfp.org/research/wecount/ "https://societyfp.org/research/wecount/"), an institution for studying abortion. In the state official report (all types of abortion), I found abortions are counted by the occurrence location of the abortion procedure or residence identity (in or out of state residents). I did not find very consistent rules for counting telehealth abortions.

>>>>

-   “All telehealth abortions are counted according to **the state the medications are mailed to**.” This approach of defining and counting telehealth aborting is used by WeCount, an institution for studying abortion. In the state official report (all types of abortion), I found abortions are counted by the occurrence location of the abortion procedure or residence identity (in or out of state residents). I did not find very consistent rules for counting telehealth abortions.
